Appendix A

### 2020-10-05 appendixA/appendixA.Rmd
individual level is ready

@@

## Probability distribution parameters
We can compare the different parameter values estimated for each distribution and their standard deviations. These parameters can give us some insight into some of the characteristics of each set of distances moved per minute, such as which individuals have higher means or longer tails in the distribution of their distances moved per minute. The x axis in the following plots highlights which individuals have the lowest BIC with that model. The blue lines show the value of that parameter for the population level model, and dashed blue lines show the upper and lower limits of that parameter estimate. Overall, at the population level, the lognormal model had the lowest BIC value.

@@

Summary: When comparing population vs individual level fits, at the population level, the lognormal distribution fits the data better, and at the individual level it is the exponential distribution. When we focus only on the individual level fits, which distribution fits best depends on the information criteria considered, although most of the individuals are properly characterized by an exponential or lognormal distribution. What we consider as the multi distribution, it is a multi-distribution probability fit to the data in which we have allowed not only the parameters but also the shape of the distribution to vary between individuals. This means that each individual can be characterized by a different distribution and different parameters. In the case of AIC and AICc, this probability approach works best for the data, however when considering BIC, the lognormal fit is best, and the mixed distribution approach ties with a weibull distribution at population level. Using BIC, a population level modeling approach is the best.

@@

## Population level - restricted
Keep in mind that the family level data is reduced because some individuals had unknown family groups and therefore are not included in this analysis.This means that we cannot directly compare distribution fits from family level aggregation with that of individuals. To make a comparisson with the population, we need to keep only data points for which we have family information

>>>>

data_gt$delta_BIC_within[which(data_gt$dist == "Multidist")] <- NA
data_gt$delta_AIC_within[which(data_gt$dist == "Multidist")] <- NA

@@

## Probability distribution parameters
We can compare the different parameter values estimated for each distribution and their standard deviations. These parameters can give us some insight into some of the characteristics of each set of distances moved per minute, such as which individuals have higher means or longer tails in the distribution of their distances moved per minute. The x axis in the following plots highlights which individuals have the lowest BIC (yellow) or AIC(magenta) with that model. The blue lines show the value of that parameter for the population level model, and dashed blue lines show the upper and lower limits of that parameter estimate. Overall, at the population level, the lognormal model had the lowest AIC and BIC values.

@@

Summary: When comparing population vs individual level fits, at the population level, the lognormal distribution fits the data better, and at the individual level it is the exponential distribution. This is shown by both AIC and BIC levels. When we focus only on the individual level fits, which distribution fits best depends on the information criteria considered, although most of the individuals are properly characterized by an exponential or lognormal distribution. What we consider as the multi distribution, it is a multi-distribution probability fit to the data in which we have allowed not only the parameters but also the shape of the distribution to vary between individuals. This means that each individual can be characterized by a different distribution and different parameters. In the case of AIC and AICc, this probability approach works best for the data, however when considering BIC, the lognormal fit is best, and the mixed distribution approach ties with a Weibull distribution at population level.

@@

## Population level - restricted
Keep in mind that the family level data is reduced because some individuals had unknown family groups and therefore are not included in this analysis.This means that we cannot directly compare distribution fits from family level aggregation with that of individuals. To make a comparison with the population, we need to keep only data points for which we have family information
